PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
edgi added adhd and personality disorder

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.body_dysmorphic_disorder_bdd_numeric = demographics.body_dysmorphic_disorder,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
#    mhd.personality_disorder_diagnosed = demographics.personality_disorder_diagnosed, # does not exist in EDGI because it is multiple choice in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

### Personality disorders
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r mhd personality_cluster_a}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(personality_cluster_a,
       cumul = F)
```

```{r Check personality_cluster_a}
mhd.raw.id %>%
  select(
    personality_cluster_a,
    personality_cluster_a_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
```

@@

```{r mhd personality_cluster_b}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_b_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(personality_cluster_b,
       cumul = F)
```

```{r Check personality_cluster_b}
mhd.raw.id %>%
  select(
    personality_cluster_b,
    personality_cluster_b_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
```

Cluster C
8. Avoidant/anxious                133 ( 4.7%)
9. Dependent                        29 ( 1.0%)
10. Obsessive-compulsive
```{r glad mhd personality_cluster_c}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_c_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 1,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(personality_cluster_c,
       cumul = F)
```

```{r Check personality_cluster_c}
mhd.raw.id %>%
  select(
    personality_cluster_c,
    personality_cluster_c_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
```

>>>>

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
#    mhd.personality_disorder_diagnosed = demographics.personality_disorder_diagnosed, # does not exist in EDGI because it is multiple choice in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    mhd.personality_disorder = demographics.personality_disorder,
    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

### Personality disorders
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r mhd personality_cluster_a}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(personality_cluster_a,
       cumul = F)
}
```

```{r Check personality_cluster_a}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    personality_cluster_a,
    personality_cluster_a_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
}
```

@@

```{r mhd personality_cluster_b}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_b_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(personality_cluster_b,
       cumul = F)
}
```

```{r Check personality_cluster_b}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    personality_cluster_b,
    personality_cluster_b_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
}
```

Cluster C
8. Avoidant/anxious                133 ( 4.7%)
9. Dependent                        29 ( 1.0%)
10. Obsessive-compulsive
```{r glad mhd personality_cluster_c}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_c_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 1,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(personality_cluster_c,
       cumul = F)
}
```

```{r Check personality_cluster_c}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    personality_cluster_c,
    personality_cluster_c_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
}
```
